---
title: "Assignment 3"
author: "Prajwal C N"
date: "10/8/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Weiglet Primal Solution 


Q1. Solve the problem using lpSolve or any other equivalent library in R.
```{r}
#Weiglet Primal Solution
library(lpSolveAPI)

lprec<-make.lp(0,9)
lp.control(lprec,sense='max')

# Objective function with 9 decision variables
set.objfn(lprec,rep(c(420,360,300),3))  

# Total there are 11 Constraints
add.constraint(lprec,c(1,1,1),"<=",750,indices = c(1,2,3))
add.constraint(lprec,c(1,1,1),"<=",900,indices = c(4,5,6))
add.constraint(lprec,c(1,1,1),"<=",450,indices = c(7,8,9))
add.constraint(lprec,c(20,15,12),"<=",13000,indices = c(1,2,3))
add.constraint(lprec,c(20,15,12),"<=",12000,indices = c(4,5,6))
add.constraint(lprec,c(20,15,12),"<=",5000,indices = c(7,8,9))
add.constraint(lprec,c(1,1,1),"<=",900,indices = c(1,4,7))
add.constraint(lprec,c(1,1,1),"<=",1200,indices = c(2,5,8))
add.constraint(lprec,c(1,1,1),"<=",750,indices = c(3,6,9))
add.constraint(lprec,c(rep(c(900,-750),each=3)),"=",0,indices = c(1,2,3,4,5,6))
add.constraint(lprec,c(rep(c(450,-750),each=3)),"=",0,indices = c(1,2,3,7,8,9))
```


Solve LP problem
```{r}
solve(lprec)
```
Output of above solve is 0,So an optimal solution was obtained


Now we can get the value of the objective function, and the variables.
```{r}
get.objective(lprec)
get.constraints(lprec)
get.variables(lprec)
```
From the above solution, we can infer the following :
Plant 1 : 516.67 of Large Products and 177.78 of Medium Products.
Plant 2 : 666.67 of Medium Products and 166.67 of Small products.
Plant 3 : 416.67 of Small Products


Q2. Identify the shadow prices,dual solution and reduced costs.
```{r}
# Reduced Cost
get.sensitivity.obj(lprec)
```
Reduced cost mentioned in $objfrom and $objtill.



```{r}
# Shadow prices
get.sensitivity.rhs(lprec)
```
Shadow prices are mentioned in $duals, and the ranges for shadow price calculations present under $dualsfrom and $dualstill.



Q3. Further,identify the sensitivity of the above prices and costs.That is,specify the range of shadow prices and reduced cost within which the optimal solution will not change
```{r}
s1 <- data.frame(get.sensitivity.rhs(lprec)$duals[1:11],get.sensitivity.rhs(lprec)$dualsfrom[1:11],get.sensitivity.rhs(lprec)$dualstill[1:11])
names(s1)<-c("price","lower","upper")
s2 <- data.frame(get.sensitivity.rhs(lprec)$duals[12:20],get.sensitivity.rhs(lprec)$dualsfrom[12:20],get.sensitivity.rhs(lprec)$dualstill[12:20])
names(s2)<-c("cost","lower","upper")

s1
s2
```
sensitivity of the above prices and costs are mentioned the range of shadow prices comprising of $dualsfrom and $dualstill.


The above is the range of shadow prices within which the optimal solution will not change.



Q4. Formulation of the dual of the above problem 

## Duality theory
```{r}
#Duality theory
library(lpSolveAPI)
lprec<-make.lp(0,11)
lp.control(lprec,sense='min')
# Objective function
set.objfn(lprec,c(750,900,450,13000,12000,5000,900,1200,750,0,0)) 

add.constraint(lprec,c(1,20,1,900,450),">=",420,indices = c(1,4,9,10,11))
add.constraint(lprec,c(1,15,1,900,450),">=",360,indices = c(1,4,8,10,11))
add.constraint(lprec,c(1,12,1,900,450),">=",300,indices = c(1,4,7,10,11))
add.constraint(lprec,c(1,20,1,-750),">=",420,indices = c(2,5,9,10))
add.constraint(lprec,c(1,15,1,-750),">=",360,indices = c(2,5,8,10))
add.constraint(lprec,c(1,12,1,-750),">=",300,indices = c(2,5,7,10))
add.constraint(lprec,c(1,20,1,-750),">=",420,indices = c(3,6,9,11))
add.constraint(lprec,c(1,15,1,-750),">=",360,indices = c(3,6,8,11))
add.constraint(lprec,c(1,12,1,-750),">=",300,indices = c(3,6,7,11))

set.bounds(lprec,lower = c(-Inf,-Inf),columns = 10:11)
```


Solve LP problem
```{r}
solve(lprec)
```
Output of above solve is 0,So an optimal solution was obtained


Now we can get the value of the objective function, and the variables.
```{r}
get.objective(lprec)
get.constraints(lprec)
get.variables(lprec)
```



```{r}
# reduced costs
get.sensitivity.obj(lprec)
```
Reduced cost mentioned in $objfrom and $objtill.

The above is the range of Reduced cost within which the optimal solution will not change.


```{r}
# shadow prices
get.sensitivity.rhs(lprec)
```
Shadow prices are mentioned in $duals, and the ranges for shadow price calculations present under $dualsfrom and $dualstill.

The above is the range of shadow prices within which the optimal solution will not change.


**The Formulation of dual solution agrees with primal solution.**